---
title: "Beans and Pods"
author: "Deckard"
date: "4/20/2021"
output: html_document
---


```{r}
#Loading Libraries
library(tidyr)
library(dplyr)
library(ggplot2)
library(readxl)
library(ggplot2)
library(ggrepel)
library(plotly)

```

Questions
where is beans and pods making the most money?
Five simple questions
1) which region is most popular?
2) is online or store more popular?
3) where are the most profitable channels?
4) which product is bought the most?
5) should we grow our online or store sales?


## Import Data


```{r}
  beans_pods <- read_excel("DS Intern - Beans Data Set.xlsx")
  head(beans_pods)
  tail(beans_pods)
  glimpse(beans_pods)

```
## Filter out rows with NA
```{r}
  filteredBeans_Pods <- filter(beans_pods, !is.na(Channel))
  nrow(beans_pods)
  nrow(filteredBeans_Pods)

```
Successfully filtered out NAs!

```{r}
str(filteredBeans_Pods)

```
## Add a variable calculating the sum of all beans and pods sold
```{r}
Beans_Pods_transformed <- filteredBeans_Pods %>% mutate(Total = Robusta + Arabica + Espresso + Lungo + Latte + Cappuccino) %>% mutate(id = row_number(), .before = Channel) # also adding an id column here

```

## Are the majority of customers coming from Online or Store?
```{r}
ggplot(filteredBeans_Pods) + 
  geom_bar(aes(x = Channel, fill = Channel)) + ylab("Transactions") + coord_flip() + theme_minimal()

```
## Which Region is most popular?
```{r}
ggplot(filteredBeans_Pods) + 
  geom_bar(aes(x = Region, fill = Region)) + ylab("Transactions") + coord_flip() + theme_minimal()

```
## Who are the most valuable customers?
```{r}
top_ten_channels <- Beans_Pods_transformed %>% top_n(10, Total)
#here are the top 10 most lucrative sales Beans & Pods has made in this dataset.
ggplot(top_ten_channels, aes(x = Region, y = Total)) +
  geom_point() +
  geom_text(aes(x = Region, label = id), size = 4, hjust = 2)  + ylab("Total Beans&Pods Sold") + theme_minimal()

#Beans&Pods made great sales with these channels. The company should reach out them with promotions and/or feedback. 
```
## Should we grow our online or store sales?
```{r}
scatter <- Beans_Pods_transformed %>%
  ggplot(aes(x = id, y = Total, fill = Channel)) +
  geom_point(alpha = 0.3) + theme_minimal()

ggplotly(scatter)

#From this plot it is easy to spot that even though there are more store sales overall. Customers who shop online purchase more beans&pods with their transactions. To maximize profit the company should look into expanding online sales.   
```
